Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-21 doc/PRF2022/PRF_main.tex
yny July20 12

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
 The streamlines are plotted in the background. 
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
  }
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the bilayer/vesicles configurations to a 
Taylor-Green (TG) background flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
 \sin\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
         {\bf e}_x
         +\sin\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
         \cos\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
             {\bf e}_y\right).
\end{equation}
The TG flow is a confining flow consisting of a checkboard pattern
of cells with alternating circulation.  We control the flow by the
the dimensionless flow strength $V_0$ and with the cell size $\lambda = l$ nm.
The default parameter $l=2$ is used through this work.
%

>>>>

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
 The streamlines are plotted in the background. 
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
  }
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the bilayer/vesicles configurations to a 
Taylor-Green (TG) background flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(\frac{{\bf e}_x\cdot\xx}{l}\right)
 \sin\left(\frac{{\bf e}_y\cdot\xx}{l}\right)
         {\bf e}_x
         +\sin\left(\frac{{\bf e}_x\cdot\xx}{l}\right)
         \cos\left(\frac{{\bf e}_y\cdot\xx}{l}\right)
             {\bf e}_y\right).
\end{equation}
The TG flow is a confining flow consisting of a checkboard pattern
of cells with alternating circulation.  We control the flow by the
the dimensionless flow strength $V_0$ and with the cell size $l$ nm.
For most of the results here the cell size $l=2$ is used in this subsection.
%
